Target Markdown

### 2024-04-04 _targets.Rmd
Update figures with interference sims

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(
  error = "null",
  packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra")
)
# Load custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
map_tibble <- tibble::tibble(
  names = c("csc_rerun", "csc_kno", "csc_non_allo", "csc_rebuild")
    )
```

@@

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(tab_sem_coeff,
    sem_main_text_coeff_csc_rerun %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

```{r, eval = FALSE}
library(targets)
tar_load_globals()
tar_load(starts_with("sim_fw_csc"))
sim_fw_csc_rerun
sim_fw_csc_rebuild
sim_fw_csc_kno
sim_fw_csc_non_allo
sim_fw_csc_non_allo
```

@@

```{r, eval = FALSE}
tar_load(sem_main_text)
tar_load(sim_fw_sem)

m <- list(
  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z, sim_fw_sem),
  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z, sim_fw_sem),
  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z, sim_fw_sem),
  async = lm(async ~ sae_total + cpe, sim_fw_sem),
  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
)

m2 <- list(
  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z + resp_div, sim_fw_sem),
  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z + env_stoch + resp_div, sim_fw_sem),
  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
  async = lm(async ~ sae_total + cpe, sim_fw_sem),
  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
)

ti <- as.psem(m)
ti2 <- as.psem(m2)
#update(ti, avg_omnivory %~~% w_avg_tlvl)
summary(ti)
summary(ti2)
tar_load(sim_fw_sem)

m3 <- list(
  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z + resp_div, sim_fw_sem),
  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z + env_stoch + resp_div, sim_fw_sem),
  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
  cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
  cpe_env = lm(cpe_env ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
  #cpe = lm(cpe ~ cpe_env + cpe_int, sim_fw_sem),
  async = lm(async ~ sae_total + cpe, sim_fw_sem),
  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
)
summary(as.psem(m3))

```{targets model-to-pred}
list(
  tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
  tar_target(model_fw_stab_comp,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
      resp = stab_com_part_var,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"),
      data = mutate(sim_fw,
      across(c(stab_com, pop_stab, async, richness), log)
      ))
        )),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
        resp = stab_com_part_var,
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"
        ),
      data = sim_fw %>%
        mutate(across(c(stab_com, richness, pop_stab, async), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, pop_stab, async, richness,
              env_stoch, resp_div, Z, c,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        )
        ))),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled_coeff,
    model_fw_stab_comp_scaled %>%
      mutate(
        coeff = map(model, function(x) {
          confint(x, level = 0.95) %>%
          as.data.frame() %>%
          rownames_to_column("term") %>%
          as_tibble() %>%
          mutate(term = str_replace(term, "cond\\.", ""))
        })
      ) %>%
      select(-model)
  ),
  tar_target(fixed_effect_fw_stab_comp,
    model_fw_stab_comp %>%
      mutate(
      fix_effect = map(model, ~fixef(.x)$cond)
      ) %>%
      select(-model)
  ),
  tar_target(default_variable_values_pred,
    c(
      "resp_div" = mean(sim_fw$resp_div),
      "env_stoch" = mean(sim_fw$env_stoch),
      "ct_alive" = mean(sim_fw$ct_alive),
      "avg_int_strength" = mean(sim_fw$avg_int_strength),
      "c" = mean(sim_fw$c),
      "w_avg_tlvl" = mean(sim_fw$w_avg_tlvl),
      "Z" = mean(sim_fw$Z)
    )
  ),
  tar_target(pred_stab_comp_resp_div,
    fixed_effect_fw_stab_comp %>%
      left_join(
        list(
          response = fixed_effect_fw_stab_comp$response,
          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
          ) %>%
        expand.grid() %>%
        left_join(
          tibble(
            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
            values = list(
              seq(quantile(sim_fw$avg_int_strength)["25%"], quantile(sim_fw$avg_int_strength)["75%"], length.out = 50),
              seq(quantile(sim_fw$w_avg_tlvl)["25%"], quantile(sim_fw$w_avg_tlvl)["75%"], length.out = 50),
              seq(quantile(sim_fw$ct_alive)["25%"], quantile(sim_fw$ct_alive)["75%"], length.out = 50)
            )
          )
        )
        ) %>%
    mutate(slope = pmap(
        list(
          param_name = variable,
          param_values = values,
          coeff = fix_effect
          ),
        function(param_name, param_values, coeff) {
          param <- list(
            seq(0, 1, length.out = length(param_values)),
            param_values
          )
          names(param) <- c("resp_div", param_name)

@@

```{r, eval = FALSE}
tar_load(sem_simplified_tot)
sem_simplified_tot %>%
  select(sim_type, collinearity) %>%
  unnest(cols = c(collinearity)) %>%
  group_by(sim_type) %>%
  summarise(
    med = median(VIF),
    max = max(VIF)
  )
tar_read(sem_main_text_eff_rerun)
```

```{targets plot-sem-tot}
list(
  tar_target(p_sem_tot_stab,
    sem_main_text_eff_tab_csc_rerun %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          alpha = response,
          ymin = lower_ci,
          ymax = upper_ci)
        ) +
      geom_pointrange() +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      #facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top")
      )
    ),
  tar_target(p_sem_tot_stab_leg,
    plot_grid(
      print(p_sem_tot_stab +
        theme(
          legend.position = "none",
        )
        ),
      get_legend(p_sem_tot_stab),
      nrow = 2,
      rel_heights = c(1, .05)
      )
  ),
  tar_target(sem_file, here("report", "figures", "sem_stab_simplified_simple.pdf"), format = "file"),
  tar_target(p_sem,
    ggdraw() +
      draw_image(magick::image_read_pdf(sem_file, density = 600),
        x = 0, y = 0,
        width = 1, height = 1,
        hjust = 0, halign = 0, valign = 0
      )
  ),
  tar_target(p_sem_fig,
    plot_grid(
      p_sem,
      print(
        tar_read(p_sem_tot_stab) +
          guides(
            color = guide_legend(override.aes = list(linetype = 0, alpha = 1)),
            y = "none",
            y.sec = "axis"
          ) +
          theme(
            legend.title = element_blank(),
            legend.position = c(.005, .995),
            legend.justification = c("left", "top"),

          )
        ),
      nrow = 2, rel_heights = c(1, .8),
      labels = "auto"
  )
  ),
  tar_target(p_sem_tot_stab_file,
    ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = print(
    p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

      )
    ),
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * .4,
  units = "mm"),
  format = "file")
)
```

```{targets plot-repro}
list(
  tar_target(p_pred_sr_resp_div,
    pred_stab_comp_resp_div %>%
      filter(response == "stab_com") %>%
      mutate(
        variable = var_replacement()[variable]
        ) %>%
      ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
      geom_raster() +
      facet_wrap(~variable, scales = "free_y") +
      coord_cartesian(expand = FALSE) +
      scale_fill_gradient2(
        low = resp_div_cat_colors()["Low"],
        mid = "white",
        high = resp_div_cat_colors()["High"],
        midpoint = 0,
        space = "Lab",
        na.value = "grey50",
        guide = "colourbar",
        aesthetics = "fill") +
      labs(
        x = var_replacement()["resp_div"],
        y = "Food-web structure",
        fill = "Slope community stability - Richness"
        ) +
      theme(
        legend.position = "bottom",
        legend.key.width = unit(2.5, "cm"),
        plot.margin = margin(l = 10, r = 10, unit = "pt")
      )
    ),
  tar_target(p_pred_sr_resp_div_file,
    ggsave_multiple(
      paste0("p_pred_sr_resp_div", c(".png", ".pdf")),
      plot = p_pred_sr_resp_div,
      path = here::here("report", "figures"),
      scale = 2.2,
      dpi = 400,
      width = 120,
      height = 120 * .45,
      units = "mm"),
    format = "file"),
  tar_target(p_pred_sr_resp_div_supp,
    pred_stab_comp_resp_div %>%
      mutate(
        variable = var_replacement()[variable],
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        ) %>%
    ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
    geom_raster() +
    facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
    coord_cartesian(expand = FALSE) +
    scale_x_continuous(
      breaks = c(0, .5, 1),
      labels = c(0, 0.5, 1)
      ) +
    scale_fill_gradient2(
      low = resp_div_cat_colors()["Low"],
      mid = "white",
      high = resp_div_cat_colors()["High"],
      midpoint = 0,
      space = "Lab",
      na.value = "grey50",
      guide = "colourbar",
      aesthetics = "fill") +
    labs(
      x = var_replacement()["resp_div"],
      y = "Food-web structure",
      fill = "Slope stability - Richness"
      ) +
    theme(
      legend.position = "bottom",
      legend.key.width = unit(2.0, "cm"),
      plot.margin = margin(l = 10, r = 10, unit = "pt")
      )),
  tar_target(p_pred_sr_resp_div_supp_file,
    ggsave_multiple(
      paste0("p_pred_sr_resp_div_supp", c(".png", ".pdf")),
      plot = p_pred_sr_resp_div_supp,
      path = here::here("report", "figures"),
      scale = 2.4,
      dpi = 400,
      width = 80,
      height = 80 * 1,
      units = "mm"),
    format = "file"
  )
)
```

@@

  tar_target(p_pop_stab_h,

@@

      ggplot(aes(x = as.factor(h), y = log(pop_stab))) +

@@

  tar_target(p_sem_bivariate_relations,

@@

      p_pop_stab_w_avg_tlvl, p_pop_stab_h, p_pop_stab_env_stoch,

@@

```{targets p-stab}
list(
  tar_target(p_cpe_env_rho, sim_fw %>%
    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
    geom_boxplot() +
    labs(x = "Response diversity", y = "Env. Compensatory effect") +
    theme_bw()),
  tar_target(p_stoch_pop_stab,
    sim_fw %>%
      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
      geom_boxplot() +
      labs(x = "Environmental stochasticity", y = "Population stability") +
      theme_bw()),
    tar_target(p_stab_comp_stress,
      plot_grid(
        p_cpe_env_rho,
        p_stoch_pop_stab,
        labels = "auto"
      )

    )
)
```

@@

>>>>

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(
  error = "null",
  packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra", "DHARMa")
)
# Load custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
map_tibble <- tibble::tibble(
  names = c("csc_rerun", "csc_kno", "csc_non_allo", "csc_rebuild")
    )
```

@@

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(tab_sem_coeff,
    sem_main_text_coeff_csc_rerun %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Response = response, Term, VIF) %>%
      kable(
        caption = "Variance Inflation Factor for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      rename(`$R^2$` = R.squared) %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

```{r, eval = FALSE}
library(targets)
tar_load_globals()
tar_load(starts_with("sim_fw_csc"))
sim_fw_csc_rerun
sim_fw_csc_rebuild
sim_fw_csc_kno
sim_fw_csc_non_allo
sim_fw_csc_non_allo
tar_read(sem_rsquared) %>%
  rename(`$R^2$` = R.squared) %>%
  kable(caption = "Rsquared for the Structural Equation Model.") %>%
  kable_styling()
```

@@

```{targets model-to-pred}
list(
  tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
  tar_target(model_fw_stab_comp,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
      resp = stab_com_part_var,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"),
      data = mutate(sim_fw,
      across(c(stab_com, pop_stab, async), log)
      ))
        )),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
        resp = stab_com_part_var,
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"
        ),
      data = sim_fw %>%
        mutate(across(c(stab_com, pop_stab, async), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, pop_stab, async, richness,
              env_stoch, resp_div, Z, c,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        )
        ))),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled_coeff,
    model_fw_stab_comp_scaled %>%
      mutate(
        coeff = map(model, function(x) {
          confint(x, level = 0.95) %>%
          as.data.frame() %>%
          rownames_to_column("term") %>%
          as_tibble() %>%
          mutate(term = str_replace(term, "cond\\.", ""))
        })
      ) %>%
      select(-model)
  ),
  tar_target(fixed_effect_fw_stab_comp,
    model_fw_stab_comp %>%
      mutate(
      fix_effect = map(model, ~fixef(.x)$cond)
      ) %>%
      select(-model)
  ),
  tar_target(default_variable_values_pred,
    c(
      "resp_div" = mean(sim_fw$resp_div),
      "env_stoch" = mean(sim_fw$env_stoch),
      "ct_alive" = mean(sim_fw$ct_alive),
      "avg_int_strength" = mean(sim_fw$avg_int_strength),
      "c" = mean(sim_fw$c),
      "w_avg_tlvl" = mean(sim_fw$w_avg_tlvl),
      "Z" = mean(sim_fw$Z)
    )
  ),
  tar_target(pred_range_fw,
    map(rlang::set_names(c("avg_int_strength", "ct_alive", "w_avg_tlvl")),
      ~quantile(sim_fw[[.x]], probs = c(.05, .95))
    )
  ),
  tar_target(pred_stab_comp_resp_div,
    fixed_effect_fw_stab_comp %>%
      left_join(
        list(
          response = fixed_effect_fw_stab_comp$response,
          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
          ) %>%
        expand.grid() %>%
        left_join(
          tibble(
            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
            values = list(
              seq(
                min(pred_range_fw$avg_int_strength),
                max(pred_range_fw$avg_int_strength),
                length.out = 50
                ),
              seq(
                min(pred_range_fw$w_avg_tlvl),
                max(pred_range_fw$w_avg_tlvl),
                length.out = 50
              ),
              seq(
                min(pred_range_fw$ct_alive),
                max(pred_range_fw$ct_alive),
                length.out = 50
              )
            )
          )
        )
        ) %>%
    mutate(slope = pmap(
        list(
          param_name = variable,
          param_values = values,
          coeff = fix_effect
          ),
        function(param_name, param_values, coeff) {
          param <- list(
            seq(0, 1, length.out = length(param_values)),
            param_values
          )
          names(param) <- c("resp_div", param_name)

@@

```{r, eval = FALSE}
tar_load(sem_main_text_tot)
sem_simplified_tot %>%
  select(sim_type, collinearity) %>%
  unnest(cols = c(collinearity)) %>%
  group_by(sim_type) %>%
  summarise(
    med = median(VIF),
    max = max(VIF)
  )
tar_read(sem_main_text_eff_rerun)
tar_load(pred_stab_comp_resp_div)
```

```{targets plot-sem-tot}
list(
  tar_target(p_sem_tot_stab,
    sem_main_text_eff_tab_csc_rerun %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          alpha = response,
          ymin = lower_ci,
          ymax = upper_ci)
        ) +
      geom_pointrange() +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      #facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top")
      )
    ),
  tar_target(p_sem_tot_stab_leg,
    plot_grid(
      p_sem_tot_stab +
        theme(
          legend.position = "none",
        ),
      get_legend(p_sem_tot_stab),
      nrow = 2,
      rel_heights = c(1, .05)
      )
  ),
  tar_target(sem_file, here("report", "figures", "sem_stab_main_text.pdf"), format = "file"),
  tar_target(p_sem,
    ggdraw() +
      draw_image(magick::image_read_pdf(sem_file, density = 600),
        x = 0, y = 0,
        width = 1, height = 1,
        hjust = 0, halign = 0, valign = 0
      )
  ),
  tar_target(p_sem_fig,
    plot_grid(
      p_sem,
      p_sem_tot_stab +
        guides(
            color = guide_legend(override.aes = list(linetype = 0, alpha = 1)),
            y = "none",
            y.sec = "axis"
          ) +
          theme(
            legend.title = element_blank(),
            legend.position = c(.005, .995),
            legend.justification = c("left", "top"),
        ),
      nrow = 2, rel_heights = c(1, .8),
      labels = "auto"
  )
  ),
  tar_target(p_sem_fig_file,
    ggsave_multiple(
      paste0("p_sem_fig", c(".png", ".pdf")),
      plot = p_sem_fig,
      path = here::here("report", "figures"),
      scale = 3.4,
      dpi = 400,
      width = 80,
      height = 80 * 1,
      units = "mm")
  ),
  tar_target(p_sem_tot_stab_file,
    ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

    ),
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * .4,
  units = "mm"))
)
```

```{targets plot-repro}
list(
  tar_target(p_pred_sr_resp_div,
    pred_stab_comp_resp_div %>%
  filter(response == "stab_com") %>%
  mutate(
    variable = var_replacement()[variable]
    ) %>%
  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y", strip.position = "left") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = resp_div_cat_colors()["Low"],
    mid = "white",
    high = resp_div_cat_colors()["High"],
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = var_replacement()["resp_div"],
    y = "Food-web structure",
    fill = "Slope community stability - Richness"
    ) +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    plot.margin = margin(l = 10, r = 10, t = 5, unit = "pt"),
    strip.placement = "outside",
    strip.background = element_blank(),
    strip.text = element_text(size = 11),
    axis.title.y = element_blank()
  )
    ),
  tar_target(p_pred_sr_resp_div_file,
    ggsave_multiple(
      paste0("p_pred_sr_resp_div", c(".png", ".pdf")),
      plot = p_pred_sr_resp_div,
      path = here::here("report", "figures"),
      scale = 2.2,
      dpi = 400,
      width = 120,
      height = 120 * .45,
      units = "mm")),
  tar_target(p_pred_sr_resp_div_supp,
    pred_stab_comp_resp_div %>%
      mutate(
        variable = var_replacement()[variable],
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        ) %>%
    ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
    geom_raster() +
    facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
    coord_cartesian(expand = FALSE) +
    scale_x_continuous(
      breaks = c(0, .5, 1),
      labels = c(0, 0.5, 1)
      ) +
    scale_fill_gradient2(
      low = resp_div_cat_colors()["Low"],
      mid = "white",
      high = resp_div_cat_colors()["High"],
      midpoint = 0,
      space = "Lab",
      na.value = "grey50",
      guide = "colourbar",
      aesthetics = "fill") +
    labs(
      x = var_replacement()["resp_div"],
      y = "Food-web structure",
      fill = "Slope stability - Richness"
      ) +
    theme(
      legend.position = "bottom",
      legend.key.width = unit(2.0, "cm"),
      plot.margin = margin(l = 10, r = 10, unit = "pt")
      )),
  tar_target(p_pred_sr_resp_div_supp_file,
    ggsave_multiple(
      paste0("p_pred_sr_resp_div_supp", c(".png", ".pdf")),
      plot = p_pred_sr_resp_div_supp,
      path = here::here("report", "figures"),
      scale = 2.4,
      dpi = 400,
      width = 80,
      height = 80 * 1,
      units = "mm")
  )
)
```

```{targets fig-stab-sr}
tar_load(default_variable_values_pred)
tar_load(model_fw_stab_comp)
tar_load(p_pred_sr_resp_div)
list(
  tar_target(richness_gradient_pred_show, seq(1, 30, length.out = 20)),
  tar_target(pred_data_show, {
    low_resp_example <- rbind(default_variable_values_pred) %>%
      as_tibble() %>%
      mutate(resp_div = .1, w_avg_tlvl = 2.0, fw_id = "new") %>%
      slice(rep(1, length(richness_gradient_pred_show))) %>%
      mutate(richness = richness_gradient_pred_show)
    high_resp_example <- rbind(default_variable_values_pred) %>%
      as_tibble() %>%
      mutate(resp_div = .9, w_avg_tlvl = 1.2, fw_id = "new") %>%
      slice(rep(1, length(richness_gradient_pred_show))) %>%
      mutate(richness = richness_gradient_pred_show)
    out <- rbind(low_resp_example, high_resp_example)
    out$stab_com <- predict(
      model_fw_stab_comp[model_fw_stab_comp$response == "stab_com", ]$model[[1]],
      out,
      allow.new.levels = TRUE
    )
    out
  }
    ),
  tar_target(p_pred_data_show_low_resp,
    pred_data_show %>%
      filter(resp_div == .1) %>%
      ggplot(aes(x = richness, y = exp(stab_com))) +
      geom_line(color = resp_div_cat_colors()["Low"]) +
      ylim(10, 25) +
      labs(x = "Species richness", y = "Community stability") +
      theme_half_open()
    ),
  tar_target(p_pred_data_show_low_resp_file,
    ggsave_multiple(
      paste0("p_pred_data_show_low_resp", c(".png", ".pdf")),
      plot = p_pred_data_show_low_resp,
      path = here::here("report", "figures"),
      scale = 1.4,
      dpi = 400,
      width = 80,
      height = 80 * .9,
      units = "mm")
    ),
  tar_target(p_pred_data_show_high_resp,
    pred_data_show %>%
      filter(resp_div == .9) %>%
      ggplot(aes(x = richness, y = exp(stab_com))) +
      geom_line(color = resp_div_cat_colors()["High"]) +
      ylim(10, 25) +
      labs(x = "Species richness", y = "Community stability") +
      theme_half_open()
    ),
  tar_target(p_pred_data_show_high_resp_file,
    ggsave_multiple(
      paste0("p_pred_data_show_high_resp", c(".png", ".pdf")),
      plot = p_pred_data_show_high_resp,
      path = here::here("report", "figures"),
      scale = 1.4,
      dpi = 400,
      width = 80,
      height = 80 * .9,
      units = "mm")
    ),
  tar_target(data_label_pred_show,
    pred_data_show %>%
      select(resp_div, richness, w_avg_tlvl) %>%
      filter(richness == min(richness)) %>%
      pivot_longer(c(w_avg_tlvl), names_to = "variable",
        values_to = "variable_values") %>%
      mutate(variable = var_replacement()[variable],
        label = c("b", "c")
      )
    ),
  tar_target(p_fig3,
    plot_grid(
      p_pred_sr_resp_div +
        theme(
          legend.position = "bottom",
          legend.title = element_text(vjust = .75),
          legend.key.width = unit(2.0, "cm")
          ) +
        geom_label(
          data = data_label_pred_show,
          aes(color = NULL, fill = NULL, label = label),
          fontface = "bold"
          ),
        plot_grid(NULL,p_pred_data_show_low_resp,
          p_pred_data_show_high_resp, NULL,
          labels = c("", "b", "c", ""), nrow = 1,
          rel_widths = c(.25, 1, 1, .25)
          ),
        labels = c("a"),
        rel_heights = c(1, .75),
        nrow = 2
    )
    ),
  tar_target(p_fig3_file,
    ggsave_multiple(
      paste0("p_fig3", c(".png", ".pdf")),
      plot = p_fig3,
      path = here::here("report", "figures"),
      scale = 2.6,
      dpi = 400,
      width = 80,
      height = 80 * .8,
      units = "mm")
  )
)
```

@@

  tar_target(p_pop_stab_c,

@@

      ggplot(aes(x = as.factor(c), y = log(pop_stab))) +

@@

  tar_target(p_raw_bivariate_relations,

@@

      p_pop_stab_w_avg_tlvl, p_pop_stab_c, p_pop_stab_env_stoch,

@@

```{targets p-stab}
list(
  tar_target(p_cpe_env_rho, sim_fw %>%
    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
    geom_boxplot() +
    labs(x = "Response diversity", y = "Env. Compensatory effect") +
    theme_bw()),
  tar_target(p_stoch_pop_stab,
    sim_fw %>%
      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
      geom_boxplot() +
      labs(x = "Environmental stochasticity", y = "Population stability") +
      theme_bw()),
    tar_target(p_stab_comp_stress,
      plot_grid(
        p_cpe_env_rho,
        p_stoch_pop_stab,
        labels = "auto"
      )
    )
)
```

@@

```{targets sem_fig_coeff, tar_simple=TRUE}
sem_main_text_eff_tab %>%
  filter(effect_type == "direct",
    predictor %in% c(
      sem_tot_predictor(),
      "async", "stab_com", "pop_stab", "sae_total", "cpe", "evenness_sae", "sae_even"
      )) %>%
select(response, predictor, effect) %>%
mutate(effect = round(effect, 2)) %>%
filter(abs(effect) >= .05)
```
